Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spread Across 400\,pc

### 2021-03-10 cluster_paper/ms.tex
lithium: fixed the interpolation bug

The third and final approach we took for age-dating the stellar
population was using the lithium deplition technique (CITE, CITE,
CITE).

Reviewing the literature, two spectroscopic datasets for \cn\ seemed
particularly important: Gaia-ESO 
\citep{randich_gaiaeso_2018} and GALAH DR3 \citep{buder_galah_2020}.
The target selection and results from each survey were as follows.

Gaia-ESO selected {\it cluster candidates} to be observed with the
GIRAFFE and UVES spectrographs based on previously reported literature
members and publicly available optical and NIR photometry.  This
target selection approach included many stars in the spatial proximity
of previously known members.  Since the possible existence of the \cn\ 
halo was not known at the time of targetting, very few ``halo'' stars
are in their ultimate sample.  For \cn, \citet{randich_gaiaeso_2018}
ultimately reported stellar parameters (including lithium equivalent
widths and metallicities) for 796 candidate members.  Cross-matching
against our kinematic list of \nkinematic candidate members by position and
imposing a 0$\farcs$5 maximum separation limit yields 492 kinematic
members for which a Gaia-ESO spectrum was acquired and stellar
parameters were reported.  15 of these (all with $(Bp-Rp)_0 > 2.0$)
are spurious matches based on the Gaia color and GES effective
temperature, and we remove them.  This yields 477 stars, of which 436
are in the core, and 41 are in the halo.  This ratio is primarily
caused by the Gaia-ESO targetting selection function.

@@

The GALAH DR3 target selection process is discussed in detail by
\citet{buder_galah_2020}.  The most relevant aspects for our project
are that the ``main'' survey targeted $12.0<V<14.0$ stars at
$\delta<+10^\circ$, provided the stars were at least ten degrees from the
galactic plane.  The survey is spatially inhomogeneous\footnote{See
the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targeting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members
for which spectra had been obtained by searching
the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after excluding
stars with the stellar parameter bit flags 1, 2, 3.  This excludes
spectra with unreliable broadening, low S/N, and unreliable wavelength
solutions (see Table~6 of \citealt{buder_galah_2020}).  Since our main
focus is measuring equivalent widths for the Li\,6708\ \AA line, these
were the most relevant bit flags for our purpose.  Of our \nkinematic
candidate \cn\ members, 106 had spectra in GALAH DR3.  51 were in the
``core''; 55 were in the ``halo''.
77 had ``finite'' lithium, i.e., no lithium flag set.

%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded\footnote{Via \url{datacentral.org.au/services/download},
using the \texttt{sobject\_id} identifiers.}
the GALAH DR3 spectra for all 106 entries.
We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.

>>>>

The third and final approach we took for confirming the youth of the
halo population of \cn\ was an analysis of the Li\,\textsc{I}
6708\,\AA doublet.  The method is reviewed by
\citet{soderblom_ages_2010}, and its connection to stellar rotation
has recently been surveyed by \citet{bouvier_lithium-rotation_2020}.
For \cn, two spectroscopic datasets  seemed particularly important:
Gaia-ESO \citep{randich_gaiaeso_2018} and GALAH DR3
\citep{buder_galah_2020}.  The target selection and results from each
survey were as follows.

Gaia-ESO selected {\it cluster candidates} to be observed with the
GIRAFFE and UVES spectrographs based on previously reported literature
members and publicly available optical and NIR photometry.  This
target selection approach included some stars in the spatial proximity
of previously known members.  Since the existence of the \cn\ halo was
not known at the time of targetting, very few ``halo'' stars are in
their sample.  For \cn, \citet{randich_gaiaeso_2018} ultimately
reported stellar parameters (including lithium equivalent widths and
metallicities) for 796 stars that they considered possible \cn\
members.  Cross-matching against our kinematic list of \nkinematic
candidate members by position and imposing a 0$\farcs$5 maximum
separation limit yields 492 kinematic members for which a Gaia-ESO
spectrum was acquired and stellar parameters were reported.  15 of
these (all with $(Bp-Rp)_0 > 2.0$) are spurious matches based on the
Gaia color and GES effective temperature, and we remove them.  This
yields 477 stars, of which 436 are in the core, and 41 are in the
halo.  The lop-sided ratio is primarily caused by the Gaia-ESO
selection function.

@@

The GALAH DR3 target selection process is discussed in detail by
\citet{buder_galah_2020}.  The most relevant aspects for our project
are that the ``main'' survey targeted $12.0<V<14.0$ stars at
$\delta<+10^\circ$, provided the stars were at least ten degrees from
the galactic plane.  The survey is spatially
inhomogeneous\footnote{See the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targeting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members for which spectra had been obtained by
searching the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after
excluding stars with the stellar parameter bit flags 1, 2, 3.  This
excludes spectra with unreliable broadening, low S/N, and unreliable
wavelength solutions (see Table~6 of \citealt{buder_galah_2020}).
Since our main focus is measuring equivalent widths for the
Li\,6708\,\AA doublet, these were the most relevant bit flags.  Of our
\nkinematic candidate \cn\ members, 107 had spectra in GALAH DR3.  51
were in the ``core''; 56 were in the ``halo''.  78 had ``finite''
lithium, i.e., no lithium flag set.

%FIXME FIXME FIXME FIXME
%FIXME FIXME FIXME FIXME

%
%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
%
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded\footnote{Via \url{datacentral.org.au/services/download},
using the \texttt{sobject\_id} identifiers.} the GALAH DR3 spectra for
all 107 entries.
We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.
